Cartogram Mapping and its Application to Cancer Data Visualization

### 2019-09-27 review_article.Rmd
Features table

|  | Choropleth | Contiguous | Non-contiguous | Dorling | Tile maps |
|:-----------:|------------|-----------|---------------|---------|-----------|
| Preserves shapes | Y | N | Y | N | N |
| Preserves neighbors | Y | Y | Y | S | S |
| Uniform use of shape | N | N | N | Y | Y |
| Bi-variate display^[A bi-variate display refers to a map that allows two variables to be plotted. One variable via the size of the area, and another by filling the area with a color.] | N | Y | Y | Y | Y |

>>>>

|  | Choropleth | Contiguous | Non-contiguous | Dorling | Tile maps | Geofacets |
|:-----------:|------------|-----------|---------------|---------|-----------|----------|
| Spatial distortion | N | Y | Y | Y | Y | Y |
| Preserves neighbors | Y | Y | Y | S | S | S |
| Conceals small areas | Y | S | N | N | N | N |
| Uniform shape | N | N | N | Y | Y | Y |
| Univariate only | Y | Y | Y | S | S | N |
| Manual construction | N | N | N | N | Y | Y |
